\documentclass[11pt]{article}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}

\title{CSCI 430 Group 11 Individual Report}
\author{Ryan Fransen-Pruden}
\date{\today}

\begin{document}

\maketitle

\section*{Introduction}
I coded the Warehouse, Waitlist, Wishlist, and Transaction classes for our group project.

\subsection*{Warehouse Class}
Responsible for managing the inventory of products. Provided methods for adding and removing products, updating quantities, and retrieving product information.

\subsection*{Waitlist Class}
Allows customers to add themselves to a waitlist for out-of-stock products. It maintains a list of customers and provided methods for adding and removing customers from the waitlist.

\subsection*{Wishlist Class}
Allows customers to create a list of products they want. Provides methods for adding and removing products from the wishlist, as well as retrieving the list of products.

\subsection*{Transaction Class}
Responsible for recording and managing customer transactions. Stores information such as the customer ID, products purchased, and the total amount.

\section*{StarID}
My StarID is: xs2548eh

\section*{Code Compilation and Testing}
To compile and test the code, follow these steps:
\begin{itemize}[label=--]
    \item Clone the project repository from GitHub:
          \begin{verbatim}
    git clone https://github.com/St-Cloud-State/warehouse-stage-i-implementation-public-void-ryan 
    \end{verbatim}
    \item Navigate to the project directory:
          \begin{verbatim}
    cd warehouse-stage-i-implementation-public-void-ryan/WarehouseStage1
    \end{verbatim}
    \item Compile the Java source files:
          \begin{verbatim}
    javac *.java
    \end{verbatim}
\end{itemize}

\end{document}